Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-20 2_SSL_EES/article/article_main.tex
added content to cost model section

>>>>

\subsection{Improvements in Manufacturing Cost}

Results of our manufacturing cost modelling for low-to-mid-power classic chip GaN phosphor-converted white LED packages are presented in Error! Reference source not found.. We find that the manufacturing cost of a single such LED decreased from 1.11\$ (in 2020 USD) in 2003 to 0.11\$ (2020 USD) in 2012 and 0.05\$ in 2020, a 95.5\% overall decrease.

Among the factors contributing to the LED cost reductions over time, improved manufacturing yields and increases in the wafer size rather than particular LED innovations are found to be responsible for the largest contribution to the overall cost reduction. In the case of manufacturing yield, the higher it is, the less inputs are wasted on the production of a single LED package. With the total manufacturing yield dramatically improving from $\sim25\%$ in 2003 to $\sim75\%$ in 2020 (compare Figure \ref{fgr:costmodel}, Panels A-C), it is not surprising that the total yielded LED manufacturing cost significantly declined over this period. In the case of wafer diameter, the larger the wafer, the more LED chips can be produced from a single wafer. The wafer diameter commonly used in LED manufacturing has been steadily increasing 2003 from 51mm (2 inch) in 2003 to 200mm ($\sim$8 inches, referred to as “8 inch") in 2020. We capture this in the model by assuming the following wafer diameters and calculating the associated number of die per wafer (DPW) \cite{de2005investigation}: $d(2003)\sim 50 mm \rightarrow851 DPW$, $d(2020)\sim200 mm \rightarrow 26,838 DPW$. With more than thirty-fold increase in the number of die per wafer between 2003 and 2020, the contribution of the whole-of-wafer processing steps to the total cost of manufacturing an individual LED chip and package has dramatically declined over time. As the number of die per wafer increases, the packaging steps, which in the classic chip architecture must be performed separately for each individual LED chip, carry a significantly larger share of the total cost in 2020 than in 2003 (compare Panels A-C in Figure \ref{fgr:costmodel}). However, as our interviewees noted, while growing LEDs on larger wafers is economically desirable, it is associated with engineering and epitaxy challenges as well as high up-front cost of new equipment.

\begin{figure*}[h!]
 \centering
 \includegraphics[width=17.5cm]{2_SSL_EES/article/figures/costmodel_results_years.pdf}
 \caption{Manufacturing cost structure modelled for a single low-to-mid power GaN, classic chip, phosphor-converted white LED package, assuming an ideal factory with state-of-the-art equipment at a U.S. location. Panels A-C: Waterfall diagrams of LED manufacturing cost split by manufacturing process steps for years 2003, 2012 and 2020. Process steps on the horizontal axis are sequenced from left to right in the same order as in the modelled LED manufacturing process. Panel F: Cumulative manufacturing yield after each process step for years 2003, 2012 and 2020. Abbreviations: Litho – Lithographic Process, Insp. – Inspection, Depn. – Deposition, CMP - Chemical-Mechanical Planarization}
 \label{fgr:costmodel}
\end{figure*}
